Fourmile

### 2024-06-14 fourmile_dataprocess.Rmd
things got weird
looking at ds3

```{r loading data, include=FALSE}
setwd('C:/Users/sears/Documents/Repos/fourmile/data')

@@

#save.image(file = 'spatial.RData')
load('C:/Users/sears/Documents/Repos/fourmile/data/spatial.RData') ## need to update with new locations + fire boundary ***

@@

hydro <- ggplot(daily_q, aes(x=date, y=q_m3s, color=site)) + geom_line() +
  ylim(0,8) + theme_bw() + 
  ggtitle('Daily streamflow (all)')

@@

>>>>

```{r loading data, include=FALSE}
setwd('/Users/megansears/Documents/Repos/fourmile/data')

@@

#save.image(file = 'spatial.RData')
load('/Users/megansears/Documents/Repos/fourmile/data/GIS/spatial.Rdata') ## need to update with new locations + fire boundary ***

@@

hydro <- ggplot(daily_q, aes(x=date, y=q_m3s, color=site)) + geom_line() +
  geom_point() +
  ylim(0,8) + 
  theme_bw() + 
  ggtitle('Daily streamflow (all)')

@@

daily_q_ds3 <- daily_q %>%
  filter(site %in% c('ds3', 'usgs1')) %>%
  mutate(year = year(date)) %>%
  filter(year %in% c(2011:2015)) %>%
  drop_na()
